Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-19 paper/ms.tex
Add caption to surface density plot

\begin{figure}[h]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-surf.pdf}
\caption{The time evolution of the gas surface density (\textit{upper}) and the star formation rate (SFR) surface density (\textit{lower}).  } \label{fig:surf}
\end{figure}

>>>>

\begin{figure}[h]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-surf.pdf}
\caption{The time evolution of the gas surface density (\textit{upper}) and
the star formation rate (SFR) surface density (\textit{lower}) at various
times during the simulation. Colored lines indicate the profiles at selected
times during the simulation while the horizontal dashed lines indicate
approximate values for the Milky Way.\cite{2012ARAA..50..531K} We see that the
gas surface density is slightly higher but within an order of magnitude of the
Milky Way's typical gas surface density. We see a sharp decrease in the gas
and SFR surface density along the extent of the bar from $\sim1$ to
$\sim4\,\textrm{kpc}$, related to the gas inflow in this region. {\color{red}
I will add the actual points from ref.\cite{2012ARAA..50..531K} (Fig. 7), but
just placing approx horizontal lines for now. The profiles are roughly flat
anyways.}}
\label{fig:surf}
\end{figure}
